R tools for accessing research literature for text mining

### 2019-08-23 manuscript.Rmd
fix #4 abstract fix

---
layout: review, 11pt
linenumbers: true
title: "R tools for accessing research literature for text mining"
author:
  - name: Scott Chamberlain
    affiliation: cstar
    email: myrmecocystus(at)gmail.com
    footnote: Corresponding author
address:
  - code: cstar
    address: |
      rOpenSci, Museum of Paleontology, University of California, Berkeley, CA, USA
abstract: |
  Text mining is a powerful method for answering research questions. However,
  getting texts to extract information can be a daunting and complicated task.
  The primary reason for this is publishers. There are thousands of different
  publishers, each with their own licenses, URL patterns, access options, and
  more. Layered on top of that is the varied access each user has based on
  their institutional affiliation. Here, I introduce a suite of software packages
  in the R programming language for fetching texts. The tapestry of different
  publishers, access levels, and other factors requires a patchwork of approaches
  for getting texts to users. The flagship R package called fulltext attempts
  to simplify search and retrieval of texts for text mining. The fulltext package,
  along with many others, make acquiring texts easier than ever, facilitating
  answering research questions with text mining.
bibliography: components/references.bib
csl: components/peerj.csl
documentclass: components/elsarticle
output:
  pdf_document:
    template: components/elsarticle.latex
    keep_tex: true
    fig_caption: true
---

>>>>

---
layout: review, 11pt
linenumbers: true
title: "R tools for accessing research literature for text mining"
author:
  - name: Scott Chamberlain
    affiliation: cstar
    email: myrmecocystus(at)gmail.com
    footnote: Corresponding author
address:
  - code: cstar
    address: |
      rOpenSci, Museum of Paleontology, University of California, Berkeley, CA, USA
abstract: |
  Text mining is a powerful method for answering research questions. However,
  getting texts to extract information can be a daunting and complicated task.
  The primary reason for this is the diversity of publisher technologies. 
  There are thousands of different publishers, each with their own licenses,
  URL patterns, access options, and more. Layered on top of that is the varied
  access each user has based on their institutional affiliation. Here, I
  introduce a suite of software packages in the R programming language for
  fetching texts. The tapestry of different publishers, access levels, and
  other factors requires a patchwork of approaches for getting texts to users.
  The flagship R package called fulltext attempts to simplify search and
  retrieval of texts for text mining by serving as an interface to the varied
  and complex publishers. The fulltext package, along with many others, make
  acquiring texts easier than ever, facilitating answering research questions
  with text mining.
bibliography: components/references.bib
csl: components/peerj.csl
documentclass: components/elsarticle
output:
  pdf_document:
    template: components/elsarticle.latex
    keep_tex: true
    fig_caption: true
---

### 2019-08-23 manuscript.tex
fix #4 abstract fix

  \begin{abstract}
  Text mining is a powerful method for answering research questions.
  However, getting texts to extract information can be a daunting and
  complicated task. The primary reason for this is publishers. There are
  thousands of different publishers, each with their own licenses, URL
  patterns, access options, and more. Layered on top of that is the varied
  access each user has based on their institutional affiliation. Here, I
  introduce a suite of software packages in the R programming language for
  fetching texts. The tapestry of different publishers, access levels, and
  other factors requires a patchwork of approaches for getting texts to
  users. The flagship R package called fulltext attempts to simplify
  search and retrieval of texts for text mining. The fulltext package,
  along with many others, make acquiring texts easier than ever,
  facilitating answering research questions with text mining.
  \end{abstract}

>>>>

  \begin{abstract}
  Text mining is a powerful method for answering research questions.
  However, getting texts to extract information can be a daunting and
  complicated task. The primary reason for this is the diversity of
  publisher technologies. There are thousands of different publishers,
  each with their own licenses, URL patterns, access options, and more.
  Layered on top of that is the varied access each user has based on their
  institutional affiliation. Here, I introduce a suite of software
  packages in the R programming language for fetching texts. The tapestry
  of different publishers, access levels, and other factors requires a
  patchwork of approaches for getting texts to users. The flagship R
  package called fulltext attempts to simplify search and retrieval of
  texts for text mining by serving as an interface to the varied and
  complex publishers. The fulltext package, along with many others, make
  acquiring texts easier than ever, facilitating answering research
  questions with text mining.
  \end{abstract}
